Evolution of vertical and oblique transmission under fluctuating selection

### 2017-12-20 ms/PNAS/revision.tex
table 1 caption alignment

\addtabletext{
\noindent $^\dagger$Note: $W=1$.\hfill\par
\noindent (a): $\rho^*$ is the uninvadable value of the vertical transmission rate.\hfill\par
\noindent (b): $\hat\rho$ is the rate that maximizes the geometric mean fitness at the stable equilibrium of the $AkBl$ cycle.\hfill}
\end{table}

>>>>

\addtabletext{
\noindent (a): \ $\rho^*$ is the uninvadable value of the vertical transmission rate.\hfill\par
\noindent (b): \ $\hat\rho$ is the rate that maximizes the geometric mean fitness at \hfill\par
\qquad\  the stable equilibrium of the $AkBl$ cycle.\hfill\par
\noindent \ \ $\dagger$:\hskip.105truein Note: $W=1$.\hfill\par
}
\end{table}
